Extracellular potentials generated by axonal projections are shaped by patterns of bifurcations and terminations

### 2016-02-19 doc/manuscript.tex
different version of pandoc on macbook

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[a4paper]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Thomas McColgan, Hermann Wagner, Richard Kempter},
            pdftitle={Extracellular potentials generated by axonal projections are shaped by patterns of bifurcations and terminations},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

@@

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  find more examples in literature
\end{itemize}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Add simplified explanations of:
\item
  spatial filtering
\item
  dipole/stationary potentials
\end{itemize}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Relevance of Findings

  \begin{itemize}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    Interpretation of CSD

    \begin{itemize}
    \itemsep1pt\parskip0pt\parsep0pt
    \item
      Classical CSD: constant fiber density, variable currents
    \item
      Here: variable fiber density, constant currents
    \end{itemize}
  \item
    Dipole has far field, ABR response?
  \end{itemize}
\item
  Compare to other auditory systems (Chicken NL, MSO)

  \begin{itemize}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    Speculate on functional relevance of polarity shift (a la Rinzel \&
    Goldwyn, Weiss 2010, Einevoll\&Panzeri review)
  \end{itemize}
\item
  Two simultaneous modes: stationary dipole and continuous (cf Mc
  Laughlin, etc).
\item
  compare to other fiber bundle systems
\end{itemize}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Split barn owl and general axon bundle
\end{itemize}

@@

\hyperdef{}{ref-Anastassiou2015Cell}{}
Anastassiou CA, Perin R, Buzsáki G, Markram H, Koch C (2015) Cell type-
and activity-dependent extracellular correlates of intracellular
spiking. Journal of Neurophysiology 114:608--623 Available at:
\url{http://dx.doi.org/10.1152/jn.00628.2014}.

\hyperdef{}{ref-Belluscio2012CrossFrequency}{}
Belluscio MA, Mizuseki K, Schmidt R, Kempter R, Buzsáki G (2012)
Cross-Frequency Phase--Phase Coupling between Theta and Gamma
Oscillations in the Hippocampus. The Journal of Neuroscience 32:423--435
Available at: \url{http://dx.doi.org/10.1523/jneurosci.4122-11.2012}.

\hyperdef{}{ref-Blot2014Ultrarapid}{}
Blot A, Barbour B (2014) Ultra-rapid axon-axon ephaptic inhibition of
cerebellar Purkinje cells by the pinceau. Nat Neurosci 17:289--295
Available at: \url{http://dx.doi.org/10.1038/nn.3624}.

\hyperdef{}{ref-Brette2012Handbook}{}
Brette R, Destexhe A eds. (2012) Handbook of Neural Activity
Measurement. Cambridge: Cambridge University Press. Available at:
\url{http://dx.doi.org/10.1017/cbo9780511979958}.

\hyperdef{}{ref-Buzsaki2012Origin}{}
Buzsáki G, Anastassiou CA, Koch C (2012) The origin of extracellular
fields and currents--EEG, ECoG, LFP and spikes. Nature reviews
Neuroscience 13:407--420 Available at:
\url{http://dx.doi.org/10.1038/nrn3241}.

\hyperdef{}{ref-carr90}{}
Carr CE, Konishi M (1990) A circuit for detection of interaural time
differences in the brain stem of the barn owl. The Journal of
Neuroscience 10:3227--3246 Available at:
\url{http://www.jneurosci.org/content/10/10/3227.abstract}.

\hyperdef{}{ref-Einevoll2013Modelling}{}
Einevoll GT, Kayser C, Logothetis NK, Panzeri S (2013) Modelling and
analysis of local field potentials for studying the function of cortical
circuits. Nature reviews Neuroscience 14:770--785 Available at:
\url{http://dx.doi.org/10.1038/nrn3599}.

\hyperdef{}{ref-FernandezRuiz2013Cytoarchitectonic}{}
Fernández-Ruiz A, Muñoz S, Sancho M, Makarova J, Makarov VA, Herreras O
(2013) Cytoarchitectonic and Dynamic Origins of Giant Positive Local
Field Potentials in the Dentate Gyrus. The Journal of Neuroscience
33:15518--15532 Available at:
\url{http://dx.doi.org/10.1523/jneurosci.0338-13.2013}.

\hyperdef{}{ref-Gold2006Origin}{}
Gold C, Henze DA, Koch C, Buzsáki G (2006) On the origin of the
extracellular action potential waveform: A modeling study. Journal of
neurophysiology 95:3113--3128 Available at:
\url{http://dx.doi.org/10.1152/jn.00979.2005}.

\hyperdef{}{ref-Goldwyn2014Model}{}
Goldwyn JH, Laughlin MM, Verschooten E, Joris PX, Rinzel J (2014) A
Model of the Medial Superior Olive Explains Spatiotemporal Features of
Local Field Potentials. The Journal of Neuroscience 34:11705--11722
Available at: \url{http://dx.doi.org/10.1523/jneurosci.0175-14.2014}.

\hyperdef{}{ref-Goodman1984Cell}{}
Goodman CS, Bastiani MJ, Doe CQ, Lac S du, Helfand SL, Kuwada JY, Thomas
JB (1984) Cell recognition during neuronal development. Science (New
York, NY) 225:1271--1279 Available at:
\url{http://view.ncbi.nlm.nih.gov/pubmed/6474176}.

\hyperdef{}{ref-Hentschel1999Models}{}
Hentschel HGE, Ooyen A van (1999) Models of axon guidance and bundling
during development. Proceedings of the Royal Society of London B:
Biological Sciences 266:2231--2238 Available at:
\url{http://dx.doi.org/10.1098/rspb.1999.0913}.

\hyperdef{}{ref-Hines1997NEURON}{}
Hines ML, Carnevale NT (1997) The NEURON Simulation Environment. Neural
Computation 9:1179--1209 Available at:
\url{http://dx.doi.org/10.1162/neco.1997.9.6.1179}.

\hyperdef{}{ref-Hines2009NEURON}{}
Hines ML, Davison AP, Muller E (2009) NEURON and Python. Frontiers in
neuroinformatics 3 Available at:
\url{http://dx.doi.org/10.3389/neuro.11.001.2009}.

\hyperdef{}{ref-Holt1999Electrical}{}
Holt GR, Koch C (1999) Electrical Interactions via the Extracellular
Potential Near Cell Bodies. Journal of Computational Neuroscience
6:169--184 Available at:
\url{http://dx.doi.org/10.1023/a:1008832702585}.

\hyperdef{}{ref-kandel2000principles}{}
Kandel ER, Schwartz JH, Jessell TM, Others (2000) Principles of neural
science. McGraw-Hill New York.

\hyperdef{}{ref-Laughlin2010Oscillatory}{}
Laughlin MM, Verschooten E, Joris PX (2010) Oscillatory Dipoles As a
Source of Phase Shifts in Field Potentials in the Mammalian Auditory
Brainstem. The Journal of Neuroscience 30:13472--13487 Available at:
\url{http://dx.doi.org/10.1523/jneurosci.0294-10.2010}.

\hyperdef{}{ref-Linden2010Intrinsic}{}
Lindén H, Pettersen K, Einevoll G (2010) Intrinsic dendritic filtering
gives low-pass power spectra of local field potentials. Journal of
computational neuroscience 29:423--444 Available at:
\url{http://dx.doi.org/10.1007/s10827-010-0245-4}.

\hyperdef{}{ref-Linden2011Modeling}{}
Lindén H, Tetzlaff T, Potjans TC, Pettersen KH, Grün S, Diesmann M,
Einevoll GT (2011) Modeling the Spatial Reach of the LFP. Neuron
72:859--872 Available at:
\url{http://dx.doi.org/10.1016/j.neuron.2011.11.006}.

\hyperdef{}{ref-Nornes1972Temporal}{}
Nornes HO, Das GD (1972) Temporal pattern of neurogenesis in spinal
cord: cytoarchitecture and directed growth of axons. Proceedings of the
National Academy of Sciences of the United States of America
69:1962--1966 Available at:
\url{http://view.ncbi.nlm.nih.gov/pubmed/4114859}.

\hyperdef{}{ref-Nunez2006Electric}{}
Nunez PL, Srinivasan R (2006) Electric Fields of the Brain. Oxford
University Press. Available at:
\url{http://dx.doi.org/10.1093/acprof:oso/9780195050387.001.0001}.

\hyperdef{}{ref-Ray2011Different}{}
Ray S, Maunsell JHR (2011) Different Origins of Gamma Rhythm and
High-Gamma Activity in Macaque Visual Cortex. PLoS Biol 9:e1000610+
Available at: \url{http://dx.doi.org/10.1371/journal.pbio.1000610}.

\hyperdef{}{ref-Reimann2013Biophysically}{}
Reimann MW, Anastassiou CA, Perin R, Hill SL, Markram H, Koch C (2013) A
Biophysically Detailed Model of Neocortical Local Field Potentials
Predicts the Critical Role of Active Membrane Currents. Neuron
79:375--390 Available at:
\url{http://dx.doi.org/10.1016/j.neuron.2013.05.023}.

\hyperdef{}{ref-Schomburg2012Spiking}{}
Schomburg EW, Anastassiou CA, Buzsáki G, Koch C (2012) The Spiking
Component of Oscillatory Extracellular Potentials in the Rat
Hippocampus. The Journal of Neuroscience 32:11798--11811 Available at:
\url{http://dx.doi.org/10.1523/jneurosci.0656-12.2012}.

\hyperdef{}{ref-Schuz2002Human}{}
Schüz A, Braitenberg V (2002) The Human Cortical White Matter. In:
Cortical areas (Schüz A, ed), pp 377--386. Abingdon, UK: Taylor \&
Francis. Available at:
\url{http://dx.doi.org/10.4324/9780203219911/_chapter/_16}.

\hyperdef{}{ref-Schwarz1992Can}{}
Schwarz DW (1992) Can central neurons reproduce sound waveforms? An
analysis of the neurophonic potential in the laminar nucleus of the
chicken. The Journal of otolaryngology 21:30--38 Available at:
\url{http://view.ncbi.nlm.nih.gov/pubmed/1564747}.

\hyperdef{}{ref-Telenczuk2011Highfrequency}{}
Teleńczuk B, Baker SN, Herz AVM, Curio G (2011) High-frequency EEG
covaries with spike burst patterns detected in cortical neurons. Journal
of Neurophysiology 105:2951--2959 Available at:
\url{http://dx.doi.org/10.1152/jn.00327.2010}.

\hyperdef{}{ref-Telenczuk2015Correlates}{}
Teleńczuk B, Baker SN, Kempter R, Curio G (2015) Correlates of a single
cortical action potential in the epidural EEG. NeuroImage 109:357--367
Available at: \url{http://dx.doi.org/10.1016/j.neuroimage.2014.12.057}.

>>>>

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[a4paper]{geometry}
\makeatletter
\@ifpackageloaded{hyperref}{}{%
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
}
\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Thomas McColgan, Hermann Wagner, Richard Kempter},
            pdftitle={Extracellular potentials generated by axonal projections are shaped by patterns of bifurcations and terminations},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}
            }
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

@@

% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\begin{itemize}
\tightlist
\item
  find more examples in literature
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  Add simplified explanations of:
\item
  spatial filtering
\item
  dipole/stationary potentials
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  Relevance of Findings

  \begin{itemize}
  \tightlist
  \item
    Interpretation of CSD

    \begin{itemize}
    \tightlist
    \item
      Classical CSD: constant fiber density, variable currents
    \item
      Here: variable fiber density, constant currents
    \end{itemize}
  \item
    Dipole has far field, ABR response?
  \end{itemize}
\item
  Compare to other auditory systems (Chicken NL, MSO)

  \begin{itemize}
  \tightlist
  \item
    Speculate on functional relevance of polarity shift (a la Rinzel \&
    Goldwyn, Weiss 2010, Einevoll\&Panzeri review)
  \end{itemize}
\item
  Two simultaneous modes: stationary dipole and continuous (cf Mc
  Laughlin, etc).
\item
  compare to other fiber bundle systems
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  Split barn owl and general axon bundle
\end{itemize}

@@

\hyperdef{}{refs}{\label{refs}}
\hyperdef{}{ref-Anastassiou2015Cell}{\label{ref-Anastassiou2015Cell}}
Anastassiou CA, Perin R, Buzsáki G, Markram H, Koch C (2015) Cell type-
and activity-dependent extracellular correlates of intracellular
spiking. Journal of Neurophysiology 114:608--623 Available at:
\url{http://dx.doi.org/10.1152/jn.00628.2014}.

\hyperdef{}{ref-Belluscio2012CrossFrequency}{\label{ref-Belluscio2012CrossFrequency}}
Belluscio MA, Mizuseki K, Schmidt R, Kempter R, Buzsáki G (2012)
Cross-Frequency Phase--Phase Coupling between Theta and Gamma
Oscillations in the Hippocampus. The Journal of Neuroscience 32:423--435
Available at: \url{http://dx.doi.org/10.1523/jneurosci.4122-11.2012}.

\hyperdef{}{ref-Blot2014Ultrarapid}{\label{ref-Blot2014Ultrarapid}}
Blot A, Barbour B (2014) Ultra-rapid axon-axon ephaptic inhibition of
cerebellar Purkinje cells by the pinceau. Nat Neurosci 17:289--295
Available at: \url{http://dx.doi.org/10.1038/nn.3624}.

\hyperdef{}{ref-Brette2012Handbook}{\label{ref-Brette2012Handbook}}
Brette R, Destexhe A eds. (2012) Handbook of Neural Activity
Measurement. Cambridge: Cambridge University Press. Available at:
\url{http://dx.doi.org/10.1017/cbo9780511979958}.

\hyperdef{}{ref-Buzsaki2012Origin}{\label{ref-Buzsaki2012Origin}}
Buzsáki G, Anastassiou CA, Koch C (2012) The origin of extracellular
fields and currents--EEG, ECoG, LFP and spikes. Nature reviews
Neuroscience 13:407--420 Available at:
\url{http://dx.doi.org/10.1038/nrn3241}.

\hyperdef{}{ref-carr90}{\label{ref-carr90}}
Carr CE, Konishi M (1990) A circuit for detection of interaural time
differences in the brain stem of the barn owl. The Journal of
Neuroscience 10:3227--3246 Available at:
\url{http://www.jneurosci.org/content/10/10/3227.abstract}.

\hyperdef{}{ref-Einevoll2013Modelling}{\label{ref-Einevoll2013Modelling}}
Einevoll GT, Kayser C, Logothetis NK, Panzeri S (2013) Modelling and
analysis of local field potentials for studying the function of cortical
circuits. Nature reviews Neuroscience 14:770--785 Available at:
\url{http://dx.doi.org/10.1038/nrn3599}.

\hyperdef{}{ref-FernandezRuiz2013Cytoarchitectonic}{\label{ref-FernandezRuiz2013Cytoarchitectonic}}
Fernández-Ruiz A, Muñoz S, Sancho M, Makarova J, Makarov VA, Herreras O
(2013) Cytoarchitectonic and Dynamic Origins of Giant Positive Local
Field Potentials in the Dentate Gyrus. The Journal of Neuroscience
33:15518--15532 Available at:
\url{http://dx.doi.org/10.1523/jneurosci.0338-13.2013}.

\hyperdef{}{ref-Gold2006Origin}{\label{ref-Gold2006Origin}}
Gold C, Henze DA, Koch C, Buzsáki G (2006) On the origin of the
extracellular action potential waveform: A modeling study. Journal of
neurophysiology 95:3113--3128 Available at:
\url{http://dx.doi.org/10.1152/jn.00979.2005}.

\hyperdef{}{ref-Goldwyn2014Model}{\label{ref-Goldwyn2014Model}}
Goldwyn JH, Laughlin MM, Verschooten E, Joris PX, Rinzel J (2014) A
Model of the Medial Superior Olive Explains Spatiotemporal Features of
Local Field Potentials. The Journal of Neuroscience 34:11705--11722
Available at: \url{http://dx.doi.org/10.1523/jneurosci.0175-14.2014}.

\hyperdef{}{ref-Goodman1984Cell}{\label{ref-Goodman1984Cell}}
Goodman CS, Bastiani MJ, Doe CQ, Lac S du, Helfand SL, Kuwada JY, Thomas
JB (1984) Cell recognition during neuronal development. Science (New
York, NY) 225:1271--1279 Available at:
\url{http://view.ncbi.nlm.nih.gov/pubmed/6474176}.

\hyperdef{}{ref-Hentschel1999Models}{\label{ref-Hentschel1999Models}}
Hentschel HGE, Ooyen A van (1999) Models of axon guidance and bundling
during development. Proceedings of the Royal Society of London B:
Biological Sciences 266:2231--2238 Available at:
\url{http://dx.doi.org/10.1098/rspb.1999.0913}.

\hyperdef{}{ref-Hines1997NEURON}{\label{ref-Hines1997NEURON}}
Hines ML, Carnevale NT (1997) The NEURON Simulation Environment. Neural
Computation 9:1179--1209 Available at:
\url{http://dx.doi.org/10.1162/neco.1997.9.6.1179}.

\hyperdef{}{ref-Hines2009NEURON}{\label{ref-Hines2009NEURON}}
Hines ML, Davison AP, Muller E (2009) NEURON and Python. Frontiers in
neuroinformatics 3 Available at:
\url{http://dx.doi.org/10.3389/neuro.11.001.2009}.

\hyperdef{}{ref-Holt1999Electrical}{\label{ref-Holt1999Electrical}}
Holt GR, Koch C (1999) Electrical Interactions via the Extracellular
Potential Near Cell Bodies. Journal of Computational Neuroscience
6:169--184 Available at:
\url{http://dx.doi.org/10.1023/a:1008832702585}.

\hyperdef{}{ref-kandel2000principles}{\label{ref-kandel2000principles}}
Kandel ER, Schwartz JH, Jessell TM, Others (2000) Principles of neural
science. McGraw-Hill New York.

\hyperdef{}{ref-Laughlin2010Oscillatory}{\label{ref-Laughlin2010Oscillatory}}
Laughlin MM, Verschooten E, Joris PX (2010) Oscillatory Dipoles As a
Source of Phase Shifts in Field Potentials in the Mammalian Auditory
Brainstem. The Journal of Neuroscience 30:13472--13487 Available at:
\url{http://dx.doi.org/10.1523/jneurosci.0294-10.2010}.

\hyperdef{}{ref-Linden2010Intrinsic}{\label{ref-Linden2010Intrinsic}}
Lindén H, Pettersen K, Einevoll G (2010) Intrinsic dendritic filtering
gives low-pass power spectra of local field potentials. Journal of
computational neuroscience 29:423--444 Available at:
\url{http://dx.doi.org/10.1007/s10827-010-0245-4}.

\hyperdef{}{ref-Linden2011Modeling}{\label{ref-Linden2011Modeling}}
Lindén H, Tetzlaff T, Potjans TC, Pettersen KH, Grün S, Diesmann M,
Einevoll GT (2011) Modeling the Spatial Reach of the LFP. Neuron
72:859--872 Available at:
\url{http://dx.doi.org/10.1016/j.neuron.2011.11.006}.

\hyperdef{}{ref-Nornes1972Temporal}{\label{ref-Nornes1972Temporal}}
Nornes HO, Das GD (1972) Temporal pattern of neurogenesis in spinal
cord: cytoarchitecture and directed growth of axons. Proceedings of the
National Academy of Sciences of the United States of America
69:1962--1966 Available at:
\url{http://view.ncbi.nlm.nih.gov/pubmed/4114859}.

\hyperdef{}{ref-Nunez2006Electric}{\label{ref-Nunez2006Electric}}
Nunez PL, Srinivasan R (2006) Electric Fields of the Brain. Oxford
University Press. Available at:
\url{http://dx.doi.org/10.1093/acprof:oso/9780195050387.001.0001}.

\hyperdef{}{ref-Ray2011Different}{\label{ref-Ray2011Different}}
Ray S, Maunsell JHR (2011) Different Origins of Gamma Rhythm and
High-Gamma Activity in Macaque Visual Cortex. PLoS Biol 9:e1000610+
Available at: \url{http://dx.doi.org/10.1371/journal.pbio.1000610}.

\hyperdef{}{ref-Reimann2013Biophysically}{\label{ref-Reimann2013Biophysically}}
Reimann MW, Anastassiou CA, Perin R, Hill SL, Markram H, Koch C (2013) A
Biophysically Detailed Model of Neocortical Local Field Potentials
Predicts the Critical Role of Active Membrane Currents. Neuron
79:375--390 Available at:
\url{http://dx.doi.org/10.1016/j.neuron.2013.05.023}.

\hyperdef{}{ref-Schomburg2012Spiking}{\label{ref-Schomburg2012Spiking}}
Schomburg EW, Anastassiou CA, Buzsáki G, Koch C (2012) The Spiking
Component of Oscillatory Extracellular Potentials in the Rat
Hippocampus. The Journal of Neuroscience 32:11798--11811 Available at:
\url{http://dx.doi.org/10.1523/jneurosci.0656-12.2012}.

\hyperdef{}{ref-Schuz2002Human}{\label{ref-Schuz2002Human}}
Schüz A, Braitenberg V (2002) The Human Cortical White Matter. In:
Cortical areas (Schüz A, ed), pp 377--386. Abingdon, UK: Taylor \&
Francis. Available at:
\url{http://dx.doi.org/10.4324/9780203219911/_chapter/_16}.

\hyperdef{}{ref-Schwarz1992Can}{\label{ref-Schwarz1992Can}}
Schwarz DW (1992) Can central neurons reproduce sound waveforms? An
analysis of the neurophonic potential in the laminar nucleus of the
chicken. The Journal of otolaryngology 21:30--38 Available at:
\url{http://view.ncbi.nlm.nih.gov/pubmed/1564747}.

\hyperdef{}{ref-Telenczuk2011Highfrequency}{\label{ref-Telenczuk2011Highfrequency}}
Teleńczuk B, Baker SN, Herz AVM, Curio G (2011) High-frequency EEG
covaries with spike burst patterns detected in cortical neurons. Journal
of Neurophysiology 105:2951--2959 Available at:
\url{http://dx.doi.org/10.1152/jn.00327.2010}.

\hyperdef{}{ref-Telenczuk2015Correlates}{\label{ref-Telenczuk2015Correlates}}
Teleńczuk B, Baker SN, Kempter R, Curio G (2015) Correlates of a single
cortical action potential in the epidural EEG. NeuroImage 109:357--367
Available at: \url{http://dx.doi.org/10.1016/j.neuroimage.2014.12.057}.
